A Triple Origin for Twin Blue Stragglers in Close Binaries

### 2019-04-01 BSS7782.tex
updates for referee report #3

We propose a formation mechanism for twin blue stragglers (BSs) in
compact binaries that involves mass transfer from an evolved outer
tertiary companion on to the inner binary via a circumbinary disk.  We
apply this scenario to the observed double BS-binary WOCS~7782 in the
old open cluster NGC~188, and show that its observed properties
\textbf{can be} reproduced within the context of the proposed model.
Based on this model, we predict the following properties for twin BSs:
(1) For the outer tertiary orbit, the initial orbital period should
lie between 220 days $\lesssim$ P$_{\rm out}$ $\lesssim$ 1100 days,
assuming initial masses for the inner binary components of $m_{\rm 1}
= 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.7$ to $0.9$M$_{\odot}$ and an
outer tertiary mass of $m_{\rm 3} = 1.4$ M$_{\odot}$.  \textbf{(2)}
After Roche-lobe overflow, the outer star turns into a white dwarf
(WD) of mass 0.43 to 0.54\,\MSun. There is a correlation between the
mass of this WD and the outer orbital period: more massive WDs will be
on wider orbits.  (3) The rotational axes of both BSs will be aligned
with each other and the orbital plane of the outer tertiary WD. (4)
The BSs will have roughly equal masses, independent of their initial
masses (since the lower mass star accretes the most).  The dominant
accretor should, therefore, be enriched more effectively by the
accreted material.  As a result, one of the BSs will appear to be more
enriched by either He, C and O or by s-process elements, depending on
whether the donor started to overflow its Roche lobe on, respectively,
the red giant or {\bf early} asymptotic giant branch.  (5) Relative to
old dense clusters with high-velocity dispersions, twin BSs in close
binaries formed from the proposed mechanism should be more frequent in
the Galactic field and younger open clusters with ages $\lesssim$ 4-6
Gyr, since then the donor will have a radiative envelope. (6) the
orbit of the binary BS will have a small semi-major axis (typically
$\aplt 0.3$\,au) and be close to circular ($e \aplt 0.1$).

@@

Even more curious, there exists in the old OC NGC 188 a double BS
binary, called WOCS 7782 \citep{2009AJ....137.3743G}.  The BS
population in NGC 188 has a bi-modal period-eccentricity distribution.
As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at
a triple origin for at least some subset of the total BS population.
As for WOCS 7782, \citet{2009Natur.462.1032M} observed a compact and
mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.
During a given binary-binary interaction, the probability that not one
but two direct (MS-MS) collisions will occur is less than $10^{-2}$
\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.
Plus, binaries with collision products typically have relatively long
orbital periods \citep{2011Sci...334.1380F}. Dynamically, it is
difficult to form a short-period binary composed of two collision
products during a collisional interaction in a star cluster
\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, \textbf{and the
  timescale for exchanging another BS into a pre-existing BS-MS or
  BS-WD binary is much longer than the expected BS lifetime (see
  \citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn}
  below)}.  So, how did WOCS 7782 form?

We propose a formation channel for WOCS 7782, and compact double BS
binaries in general, which involves mass transfer from an outer
tertiary companion on to an inner binary composed of two MS stars.  In
section~\ref{sect:dyn}, we constrain the range of initial (i.e.,
pre-mass transfer) orbital parameters for a hypothetical outer
tertiary companion, using a combination of dynamical and stellar
evolution-based constraints.  In Section~\ref{sims} we present the
numerical simulations used to study the mass transfer process in this
triple system. We adopt orbital parameters that, according to our
expectations, are most promising for the progenitors of the twin BS
7782.  The calculations are performed using the Astrophysical
Multipurpose Software Environment \cite[\texttt{AMUSE} for short,
  see][]{PortegiesZwart2013456,AMUSE} with a combination of stellar
evolution, hydrodynamical and gravitational simulations.  With these
calculations we further constrain the possible range of initial
parameters that naturally lead to twin BSs with orbital parameters
similar to the 7782 system.  We summarize and discuss the implications
of our results for compact double BS binaries and, more generally,
mass transfer in stellar triples in Section~\ref{sect:discussion}.

@@

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_M14MSun_outerorbit.pdf}
  \caption{Giant radius as a function of the mass of the core of the
    Roche-lobe filling outer star (dark blue curve).  {\bf The first
      and last parts of this curve are orange to indicate that the
      star at these masses and radii is on the Hertzsprung-gap (to the
      left) or after core helium burning stage (to the right).  Only
      when the donor is on the giant branch (dark blue) Roche-lobe
      overflow will lead to a binary blue straggler.}  Here we adopt a
    donor mass of 1.4\,\MSun, but for an 1.2\,\MSun\, the donor the
    curve is quite similar (see dotted dark-blue curve).  The red
    squares in the curve show the parameters for which we performed
    more detailed gravitational-hydrodynamical simulations (see
    \S\,\ref{sims}).  The horizontal dashed line shows the orbital
    separation of the observed twin BS 7782.  The initial triple in
    which it possibly formed must at least have been dynamically
    stable. The minimal orbital separation for the inner binary for
    which the triple is stable is given by the lower green coloured
    curve.  Donors which are smaller than about 100\,\RSun\,
    (light-green curve indicated with a$_{\rm stable}$) result in a
    dynamically unstable triple. The minimal core mass associated with
    a stable triple is then indicated by the left-most vertical dotted
    line.  The orbital separation at which the donor star overfills
    its Roche lobe is indicated with the light-blue curve. The top
    curve (brown) shows an estimate of the final orbital separation of
    the outer star, and therefore of the final orbit of the WD around
    the inner twin BSs.  For core masses $\apgt 0.5$\,\MSun\, the
    final orbital separation, after mass transfer, is smaller than the
    initial orbit.  Here we adopted an initial inner binary mass of
    (1.0+0.9)\,\MSun\, and a final twin BS mass of (1.4+1.4)\,\MSun.
\label{fig:tertiarymass_vs_size}}
\end{figure}

@@

To test the \textbf{hypothesis that the} secondary in the inner binary
accretes more effectively than the primary star and to measure the
change to the inner orbit due to the Roche-lobe overflow of the outer
star, we perform a series of calculations in which we take the self
gravity and the hydrodynamical effects of the triple into account.
The results of \textbf{one of} these simulations (1091 days after
the onset of mass transfer) is presented in
figure~\ref{fig:mass_vs_semimajor_axis}.
%% figure~\ref{fig:topview_at_t1000day} and
%% The first figure
%% (figure~\ref{fig:topview_at_t1000day}) shows the top view of the same
%% initial realization for which we presented the initial conditions in
%% figure~\ref{fig:topview_at_t0} but now at an age of 1091 days after
%% the onset of mass transfer. We add, to the left panel,
%% the equipotential surfaces in the orbital plane.

It is apparent that the mass transfer in the adopted triples leads to
a rather untidy evolution, since much of the donor mass is lost
through the second Lagrangian point to the right side of the donor
star in figure~\ref{fig:topview_at_t1000day}. A considerable amount of
mass is also lost through the third Lagrangian point (to the left of
the inner binary), although it is hard to actually \textbf{quantify
  the amount of material lost}, becuase an appreciable fraction may to
rain back onto the triple system.  One remaining question is how much
mass is eventually ejected altogether from the triple system and is
therefore not accreted to any of the two inner stars. This value is
hard to estimate from the simulations, but an accretion efficiency of
$\apgt 0.8$ is necessary to make the scenario feasible. Over the time
scale for which we performed the calculations, this efficiency is
reached, but it is not clear how the system responds at later stages.

\begin{figure*}[ht!]
  \includegraphics[width=0.5\linewidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.png}
~  \includegraphics[width=0.5\linewidth]{fig_BBSS_gas_M14Msun_A010au_t3360.png}
  \caption{ Top view of one of the simulated triple systems at an age
    of $t \simeq 1091\,days$ after the start of the simulation when
    the 100\,\RSun\, outer star of 1.4\,\MSun\, over-fills its
    Roche-lobe.  The star is represented by 80000\,SPH particles and a
    core particle of $\sim 0.4$\,\MSun (black bullet in the middle of
    the right-most yellow blob). The inner binary \textbf{(to the
      left)} is represented by the yellow and red bullets for,
    respectively, the 1.1\,\MSun\, primary and 0.9\,\MSun\, secondary
    stars in a circular orbit of 0.1\,au. The 1.4\,\MSun\, giant star
    is presented to the right in a circular orbit with semi-major axis
    $\sim 250$\,\RSun\, in the plane of the inner binary.  Left panel
    shows the equipotential surfaces of the triple overplotted with
    the gas distribution, the right panel shows just the gas and the
    stars as bullets.
\label{fig:topview_at_t1000day}}
\end{figure*}

@@

In the right-hand panel in figure~\ref{fig:mass_vs_semimajor_axis} we
present the evolution of the orbit for the 1.4\,\MSun\, donor for
several initial orbits of the inner binary. A more massive donor
appears to be more effective in producing a twin BS with parameters
consistent with the observed system 7782. There is more mass available
in the envelope of the donor star, and the orbital evolution of the
inner binary matches better with the anticipated evolution
\textbf{needed to reproduce the observed parameters of WOCS 7782.}  A
more massive donor may therefore have a lower accretion efficiency
while still accomodating the observed constraints.  The longer thermal
time scale of the stellar envelope of the higher-mass donor at the
same stellar radius eventually leads to a higher mass-transfer rate,
and therefore to a lower accretion efficiency. However, the larger
mass budget in the envelope appears to compensate.

The orbit of the inner binary expands in these cases as a result of
accretion onto the inner two stars. \textbf{In all} three cases for the
1.4\,\MSun\, donor presented in
figure~\ref{fig:mass_vs_semimajor_axis} the inner orbit expands at
about the same rate. Consequently, the inner binaries that start with
$a = 0.15$\,au and $a=0.20$\,au eventually become dynamically
unstable.  The binary with an initial separation of $0.10$\,au expands
to reach a separation of about 0.126--0.145\,au for final masses for
the inner two stars of 1.4\,\MSun, which is consistent with the
observed twin BS 7782. In our simulations the eccentricity of the
inner binary grows to about $e \simeq 0.0028$.

With the accretion of mass, both stars in the inner binary also
accrete angular momentum.  By the end of the simulation the spins of
the two BSs are aligned along the orbital angular momentum axis with
an angle of $90.0^\circ$ for the primary star and $93.4^\circ$ for the
secondary star with respect to the argument of pericenter of the inner
orbit.  \textbf{This supports our naive prediction that the spin
  angular momenta of the two stars in the inner binary should be more
  or less aligned post-mass transfer, due to the non-negligible amount
  of mass accreted.} By the end of the simulations the spin of the
primary is about 50.5 rotations per day, and 41.5 rotations per day
for the secondary star.  \textbf{Such high spin rates immediately
  post-mass transfer are supported by other work (see, for example,
  \citet{2014MNRAS.438.1909D}), which could then subsequently spin
  down due to, for example, magnetic braking, bringing them closer to
  the actually observed spin rates.}
%% But by this time both stars have accreted
%% only a small portion of mass and we expect that the final spins of
%% both stars will be close to break-up (ignoring any spin-down from
%% magnetic braking effects).

@@

\item For the predicted outer tertiary orbit, the initial orbital
  period should lie between 220 days $\lesssim$ P$_{\rm out}$
  $\lesssim$ 1100 days, assuming initial masses for the inner binary
  components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$
  M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
  $M$_{\odot}$. \textbf{The final orbital period of the white dwarf
    around the binary blue straggler should exceeds the initiall
    orbit, but be smaller than $\sim 4100$\,days.}

@@

  \textbf{ We further validated this statement by performing an
    additional series of calculations in which we vary the mass of the
    tertiary star in the initial triple from 0.5\,\MSun\, to
    0.7\,\MSun\, and 0.9\,\MSun. In
    fig.\,\ref{fig:mass_ratio_evolution_for_14MSun} we present the
    evolution of the normalized mass ratio in these binaries. with
    these calculations we demonstrate that a low-mass ratio initially
    tends to evolve towards an equal mass ratio.  }

@@

\item As a consequence of the above, the initially lower mass MS star
  should accrete the most, and therefore be more enriched by accreted
  material.  This could be observable in the surface layers of a
  radiative star.  If the donor is an RGB star, the accretors will be
  enriched in mostly carbon, oxygen and helium, but if the donor is an
  AGB star the enrichment will be mostly in s-process elements.
  \textbf{Note that part of the mass liberated from the triple system
    through the second and third Lagrangian points may eventually be
    accreted back onto the system.  This could also have interesting
    consequences for the enrichment of the low-mass white dwarf.  Such
    a debris disk was recently found around the white dwarf SDSS
    J122859.93+104032.9 \citep{Manseretal2019}.  }

\item We expect twin BSs in compact binaries formed from the mechanism
  proposed here to be more frequent in younger clusters with ages
  $\lesssim$ 4-6 Gyr.  This is because \textbf{stars in clusters} with a MS turn-off
  mass $\lesssim$ 1.2 M$_{\odot}$ have convective envelopes
  \citep[e.g.][]{1991ApJS...76...55I,2009pfer.book.....M}, and a
  radiative envelope for the donor in a mass transferring binary
  ensures stable accretion on to the accretor.

>>>>

We propose that twin blue stragglers (BSs) in compact binaries evolve
through a phase of mass transfer from a giant outer tertiary companion
on to the inner binary.  We apply this scenario to the twin-BS binary
WOCS~ID~7782 in the old open cluster NGC~188.  This binary has two
comparable-mass main-sequence stars in an almost circular ($e \aplt
0.1$) orbit of $\aplt 10$\,days.  Our theoretical arguments are
supported by simulations of an inner binary that accretes from a outer
Roche-lobe overfilling star using the Astrophysicsal Multipurpose
Software Environment. At least 80\,\% of the mass liberated by the
tertiary star goes through a circum-binary disk before it is accreted
by in the inner binary, causing the two stars to turn into blue
stragglers.  In order to acquire relatively stable phase of mass
transfer the donor should be about 1.4\,\MSun\, and over-fill it's
Roche lobe before ascending the asymptotic giant-branch.  The outer
star eventually turns into a 0.43 to 0.54\,\MSun\, white dwarf in a
relatively wide $\apgt 5.8\,yr$ orbit.  Although, the scenario is
generic, it requires some fine-tuning to achieve parameters comparable
to the observed twin WOCS~ID~7782.  This system is best reproduced
when starting with a $m_{\rm 3} = 1.4$ M$_{\odot}$ outer star in an
220 to 1100~day orbit around an inner binary composed of an
1.1\,\,MSun\, primary and a $m_{\rm 2}=0.7$ to $0.9$M$_{\odot}$
secondary star in an 8.6 to 24\,day orbit.  Based on our simulations
and theoretical arguments we predict that twin blue-stragglers that
formed through mass transfer from a Roche-lobe over-filling outer star
are generally comparable in mass, have aligned spins which again are
algined with the orbit of the tertiary white-dwarf star.  If the two
inner stars ware initially unequal in mass the less massive star will
have accreted more material from the tertiary star, which therefore is
more enhanced in CNO-processed material.

@@

Even more curious, there exists in the old OC NGC 188 a double BS
binary, called WOCS 7782 \citep{2009AJ....137.3743G}.  The BS
population in NGC 188 has a bi-modal period-eccentricity distribution.
As discussed in \citet{2011MNRAS.410.2370L}, this could be hinting at
a triple origin for at least some subset of the total BS population.
As for WOCS 7782, \citet{2009Natur.462.1032M} observed a compact and
mildly eccentric (i.e., $e \sim 0.1$) binary star system with an
orbital period of $\sim$ 10 days hosting two roughly equal-mass BSs.
During a given binary-binary interaction, the probability that not one
but two direct (MS-MS) collisions will occur is less than $10^{-2}$
\citep{1989AJ.....98..217L,2011MNRAS.410.2370L,2012MNRAS.425.2369L}.
Plus, binaries with collision products typically have relatively long
orbital periods \citep{2011Sci...334.1380F}. Dynamically, it is
difficult to form a short-period binary composed of two collision
products during a collisional interaction in a star cluster
\citep{2011MNRAS.410.2370L,2011Sci...334.1380F}, and the timescale for
exchanging another BS into a pre-existing BS-MS or BS-WD binary is
much longer than the expected BS lifetime (see
\citet{2011MNRAS.410.2370L} and the end of Section~\ref{sect:dyn}
below).  So, how did WOCS 7782 form?

We propose a formation channel for WOCS 7782, and compact double BS
binaries in general, which involves mass transfer from an outer
tertiary companion on to an inner binary composed of two MS stars.  In
section~\ref{sect:dyn}, we constrain the range of initial (i.e.,
pre-mass transfer) orbital parameters for a hypothetical outer
tertiary companion, using a combination of dynamical and stellar
evolution-based constraints.  In Section~\ref{sims} we present the
numerical simulations used to study the mass transfer process in this
triple system. We adopt orbital parameters that, according to our
expectations, are most promising for the progenitors of the twin BS
7782.  The calculations are performed using the Astrophysical
Multipurpose Software Environment \cite[\texttt{AMUSE} for short,
  see][]{PortegiesZwart2013456,AMUSE} with a combination of stellar
evolution, hydrodynamical and gravitational simulations.  With these
calculations we further constrain the possible range of initial
parameters that naturally lead to twin BSs with orbital parameters
similar to the 7782 system, without exhaustively covering parameter
space.  We summarize and discuss the implications of our results for
compact double BS binaries and, more generally, mass transfer in
stellar triples in Section~\ref{sect:discussion}.

@@

\begin{figure}[ht!]
  \includegraphics[width=\columnwidth]{fig_M14MSun_outerorbit.pdf}
  \caption{Giant radius as a function of the mass of the core of the
    Roche-lobe filling outer star (dark blue curve).  The first and
    last parts of this curve are orange to indicate that the star at
    these masses and radii is on the Hertzsprung-gap (to the left) or
    after core helium burning stage (to the right).  When the
    donor is on the giant branch (dark blue) Roche-lobe overflow will
    lead to a binary blue straggler.  Here we adopt a donor mass of
    1.4\,\MSun, but for an 1.2\,\MSun\, the donor the curve is quite
    similar (see dotted dark-blue curve).  The red squares in the
    curve show the parameters for which we performed more detailed
    gravitational-hydrodynamical simulations (see \S\,\ref{sims}).
    The horizontal dashed line shows the orbital separation of the
    observed twin BS 7782.  The initial triple in which it possibly
    formed must at least have been dynamically stable. The minimal
    orbital separation for the inner binary for which the triple is
    stable is given by the lower green coloured curve.  Donors which
    are smaller than about 100\,\RSun\, (light-green curve indicated
    with a$_{\rm stable}$) result in a dynamically unstable
    triple. The minimal core mass associated with a stable triple is
    then indicated by the left-most vertical dotted line.  The orbital
    separation at which the donor star overfills its Roche lobe is
    indicated with the light-blue curve. The top curve (brown) shows
    an estimate of the final orbital separation of the outer star, and
    therefore of the final orbit of the WD around the inner twin BSs.
    For core masses $\apgt 0.5$\,\MSun\, the final orbital separation,
    after mass transfer, is smaller than the initial orbit.  Here we
    adopted an initial inner binary mass of (1.0+0.9)\,\MSun\, and a
    final twin BS mass of (1.4+1.4)\,\MSun.
\label{fig:tertiarymass_vs_size}}
\end{figure}

@@

To test the hypothesis that the secondary in the inner binary
accretes more effectively than the primary star and to measure the
change to the inner orbit due to the Roche-lobe overflow of the outer
star, we perform a series of calculations in which we take the self
gravity and the hydrodynamical effects of the triple into account.
The results of one of these simulations (1091 days after
the onset of mass transfer) is presented in
figure~\ref{fig:mass_vs_semimajor_axis}.
%% figure~\ref{fig:topview_at_t1000day} and
%% The first figure
%% (figure~\ref{fig:topview_at_t1000day}) shows the top view of the same
%% initial realization for which we presented the initial conditions in
%% figure~\ref{fig:topview_at_t0} but now at an age of 1091 days after
%% the onset of mass transfer. We add, to the left panel,
%% the equipotential surfaces in the orbital plane.

It is apparent that the mass transfer in the adopted triples leads to
a rather untidy evolution, since much of the donor mass is lost
through the second Lagrangian point to the right side of the donor
star in figure~\ref{fig:topview_at_t1000day}. A considerable amount of
mass is also lost through the third Lagrangian point (to the left of
the inner binary), although it is hard to actually quantify the amount
of material lost, becuase an appreciable fraction may to rain back
onto the triple system.  One remaining question is how much mass is
eventually ejected altogether from the triple system and is therefore
not accreted to any of the two inner stars.  In our simulations the
accretion efficiency on the inner binary has to exceeds $\sim 80$\,\%
for the two blue straggers to reach masses comparable to those
observed in WOCS~ID~7782.  Over the relatively short time scale for
which we performed the calculations this efficiency is achieved, but
it is not clear how the system responds at later stages.

\begin{figure*}[ht!]
  \includegraphics[width=0.5\linewidth]{fig_BBSS_Lgas_M14Msun_A010au_t3360.png}
~  \includegraphics[width=0.5\linewidth]{fig_BBSS_gas_M14Msun_A010au_t3360.png}
  \caption{ Top view of one of the simulated triple systems at an age
    of $t \simeq 1091\,days$ after the start of the simulation when
    the 100\,\RSun\, outer star of 1.4\,\MSun\, over-fills its
    Roche-lobe.  The star is represented by 80000\,SPH particles and a
    core particle of $\sim 0.4$\,\MSun (black bullet in the middle of
    the right-most yellow blob). The inner binary (to the
      left) is represented by the yellow and red bullets for,
    respectively, the 1.1\,\MSun\, primary and 0.9\,\MSun\, secondary
    stars in a circular orbit of 0.1\,au. The 1.4\,\MSun\, giant star
    is presented to the right in a circular orbit with semi-major axis
    $\sim 250$\,\RSun\, in the plane of the inner binary.  Left panel
    shows the equipotential surfaces of the triple overplotted with
    the gas distribution, the right panel shows just the gas and the
    stars as bullets.
\label{fig:topview_at_t1000day}}
\end{figure*}

@@

In the right-hand panel in figure~\ref{fig:mass_vs_semimajor_axis} we
present the evolution of the orbit for the 1.4\,\MSun\, donor for
several initial orbits of the inner binary. A more massive donor
appears to be more effective in producing a twin BS with parameters
consistent with the observed system 7782. There is more mass available
in the envelope of the donor star, and the orbital evolution of the
inner binary matches better with the anticipated evolution
needed to reproduce the observed parameters of WOCS 7782.  A
more massive donor may therefore have a lower accretion efficiency
while still accomodating the observed constraints.  The longer thermal
time scale of the stellar envelope of the higher-mass donor at the
same stellar radius eventually leads to a higher mass-transfer rate,
and therefore to a lower accretion efficiency. However, the larger
mass budget in the envelope appears to compensate.

The orbit of the inner binary expands in these cases as a result of
accretion onto the inner two stars. In all three cases for the
1.4\,\MSun\, donor presented in
figure~\ref{fig:mass_vs_semimajor_axis} the inner orbit expands at
about the same rate. Consequently, the inner binaries that start with
$a = 0.15$\,au and $a=0.20$\,au eventually become dynamically
unstable.  The binary with an initial separation of $0.10$\,au expands
to reach a separation of about 0.126--0.145\,au for final masses for
the inner two stars of 1.4\,\MSun, which is consistent with the
observed twin BS 7782. In our simulations the eccentricity of the
inner binary grows to about $e \simeq 0.0028$.

With the accretion of mass, both stars in the inner binary also
accrete angular momentum.  By the end of the simulation the spins of
the two BSs are aligned along the orbital angular momentum axis with
an angle of $90.0^\circ$ for the primary star and $93.4^\circ$ for the
secondary star with respect to the argument of pericenter of the inner
orbit.  This supports our naive prediction that the spin angular
momenta of the two stars in the inner binary should be more or less
aligned post-mass transfer, due to the non-negligible amount of mass
accreted. By the end of the simulations the spin of the primary is
about 50.5 rotations per day, and 41.5 rotations per day for the
secondary star.  Such high spin rates immediately post-mass transfer
are supported by other work (see, for example,
\citet{2014MNRAS.438.1909D}), but the twin blue stragglers in
WOCS~ID~7782 are not observed to be spinning that fast
\cite{2018ApJ...869L..29L}.  Rapdily spinning stars may slow due to,
for example, magnetic braking, bringing them closer to the actually
observed spin rates \cite{2018arXiv181202181L}.

%% But by this time both stars have accreted
%% only a small portion of mass and we expect that the final spins of
%% both stars will be close to break-up (ignoring any spin-down from
%% magnetic braking effects).

@@

\item For the predicted outer tertiary orbit, the initial orbital
  period should lie between 220 days $\lesssim$ P$_{\rm out}$
  $\lesssim$ 1100 days, assuming initial masses for the inner binary
  components of $m_{\rm 1} = 1.1$ M$_{\odot}$ and $m_{\rm 2} = 0.9$
  M$_{\odot}$ and an initial outer tertiary mass of $m_{\rm 3} = 1.4
  $M$_{\odot}$. The final orbital period of the white dwarf
    around the binary blue straggler should exceeds the initial
    orbit, but be smaller than $\sim 4100$\,days.

@@

  We further validated this statement by performing an
    additional series of calculations in which we vary the mass of the
    tertiary star in the initial triple from 0.5\,\MSun\, to
    0.7\,\MSun\, and 0.9\,\MSun. In
    fig.\,\ref{fig:mass_ratio_evolution_for_14MSun} we present the
    evolution of the normalized mass ratio in these binaries. with
    these calculations we demonstrate that a low-mass ratio initially
    tends to evolve towards an equal mass ratio.

@@
